Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
generate SR

# Cluster level
statistics_cluster <- d_transcript %>%
  inner_join(
    d_course, 
    by = "Course ID"
    ) %>%
  provide_statistics(Cluster)

# Type level
statistics_type <- d_transcript %>%
  inner_join(
    d_course, by = "Course ID"
    ) %>%
  provide_statistics(Type)

# Concentration evel
statistics_concentration <- d_transcript %>%
  inner_join(
    d_course,
    by = "Course ID"
    ) %>%
  gather(
    key = X, 
    value = Concentration, 
    Concentration, `Concentration (additional)`,
    na.rm = TRUE
    ) %>%
  provide_statistics(Concentration)

# Year level
statistics_year <- d_transcript %>%
  provide_statistics(Year_numerical)

# Level level
statistics_level <- d_transcript %>%
  # TODO: filter for student who completed their studies
  inner_join(d_course, by = c("Course ID")) %>%
  provide_statistics(Level)

@@

### take -> taken
```{r AR take}
AR <- list()

@@

### less than x grade -> less than 6
```{r AR grade}
AR$G <- transactions$G %>%

@@

## Sequence Rules

@@

@@

```{r SR edit}
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
```

We generate sequence rules:
```{r SR taken, cache = TRUE}

#Generating sequence rules:
SR_taken   <- my_SR(data = sequences$taken)
```

```{r SR PF, cache = TRUE}

##pass/fail filter
SR_PF      <- my_SR(data = sequences$PF) %>%
  filter(
    str_detect(rhs, "fail"),
    str_detect(lhs, "fail")
    )
```

```{r SR HL, cache = TRUE}

##high/low filter
SR_HL      <- my_SR(data = sequences$HL) %>% 
  filter(
    str_detect(rhs, "low"),
    str_detect(lhs, "low")
    )
```

```{r SR grade, cache = TRUE}

SR_G   <- my_SR(data = sequences$G )
```

```{r SR grade exp, cache = TRUE}

#Grades filter 
#SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
```

>>>>

# Cluster level
statistics$cluster <- d_transcript %>%
  inner_join(
    d_course, 
    by = "Course ID"
    ) %>%
  provide_statistics(Cluster)

# Type level
statistics$type <- d_transcript %>%
  inner_join(
    d_course, by = "Course ID"
    ) %>%
  provide_statistics(Type)

# Concentration evel
statistics$concentration <- d_transcript %>%
  inner_join(
    d_course,
    by = "Course ID"
    ) %>%
  gather(
    key = X, 
    value = Concentration, 
    Concentration, `Concentration (additional)`,
    na.rm = TRUE
    ) %>%
  provide_statistics(Concentration)

# Year level
statistics$year <- d_transcript %>%
  provide_statistics(Year_numerical)

# Level level
statistics$level <- d_transcript %>%
  # TODO: filter for student who completed their studies
  inner_join(d_course, by = c("Course ID")) %>%
  provide_statistics(Level)

@@

### take -> take
```{r AR take}
AR <- list()

@@

### grade less than or equal to x -> grade less than or equal to 6
```{r AR grade}
AR$G <- transactions$G %>%

@@

## Sequence Rules
### Functions

@@

```{r}
make_SR <- function(data){

  data %>%
    my_cspade %>%
    my_ruleInduction %>%
    clean_SR

### take -> take
```{r}
SR <- list()

SR$taken <- sequences$taken %>%
  my_SR
```

### fail -> fail
```{r}
SR$PF <- sequences$PF %>%

  my_SR %>%

  # lhs and rhs are fail
  filter(
    str_detect(lhs, "fail"),
    str_detect(rhs, "fail")
    )
```

### low grade -> low grade
```{r}
SR$HL <- sequences$HL %>%

  my_SR %>%

  # lhs and rhs are low
  filter(
    str_detect(lhs, "low"),
    str_detect(rhs, "low")
    )
```

### not take -> fail
```{r}
# by hand
```

### grade less than or equal to x -> grade less than or equal to 6
```{r}
SR$G <- sequences$G %>%

  my_SR %>%

  # rhs is grade less than 6
  filter(
    str_detect(rhs, "6")
    )
```

### Editing AR
```{r SR edit}
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
```

### Save Sequences Rules

@@
